Double White Dwarf Mergers with CASTRO\\ I. Methodology and Code Verification

### 2015-10-02 documentation/userguide.tex

The \texttt{tests} directory includes problem setups that are used for testing 
the hydrodynamics code \texttt{CASTRO} and exercises a wide range of its capabilities.

@@

The routines that generate both of these are found in \\\texttt{source/diagnostics/sum\_integrated\_quantities.cpp}. 
This is a replacement of the \texttt{CASTRO} function that does something similar. We use the same 
conventions; for example, if summing over the whole grid and we encounter a region that is covered by 
a fine grid, we zero out the contribution from the coarse grid and only count the fine grid quantities 
in that location.

@@

If you want to build your own problem setup, you can do that too. The job submission 
requirements are the same as in Section \ref{sec:standard_problems}, but you will need to provide 
your own source files and makefile. They can go in the \texttt{compile/} subdirectory in your problem location.
At minimum, you'll need a \texttt{Prob\_3d.f90} file (or the equivalent for lower dimensions) and
corresponding inputs and probin files. The problems in \texttt{tests/castro} are similar to this;
they are ultimately building using the source code in the CASTRO test suite, but using a
\texttt{run\_test.sh} that is very similar to the one used for merger problems.

@@

The \texttt{tests} directory contains a number of example problems that we use
to assess the reliability of \texttt{CASTRO} in performing hydrodynamics simulations 
with self-gravity. This section includes a list of the existing problems 
as well as the instructions for building and running a problem.

>>>>

The \texttt{science} directory includes problem setups that are or have been used in the papers
that have been or will be submitted based on this software.

The \texttt{tests} directory is designed to hold small versions of problems that can be run in a
nightly test suite that regularly checks for code errors.

@@

The routines that generate both of these are found in \\\texttt{source/sum\_integrated\_quantities.cpp}. 
This is a replacement of the \texttt{CASTRO} function that does something similar. We use the same 
conventions; for example, if summing over the whole grid and we encounter a region that is covered by 
a fine grid, we zero out the contribution from the coarse grid and only count the fine grid quantities 
in that location.

@@

If you want to build your own problem setup, you can do that too. The job submission 
requirements are the same as in Section \ref{sec:standard_problems}, but you will need to provide 
your own source files and makefile. They can go in the \texttt{compile/} subdirectory in your problem location.
At minimum, you'll need a \texttt{Prob\_3d.f90} file (or the equivalent for lower dimensions) and
corresponding inputs and probin files. The problems in \texttt{science/wdmerger_I/castro} are similar to this;
they are ultimately building using the source code in the CASTRO test suite, but using a
\texttt{run\_test.sh} that is very similar to the one used for merger problems.

@@

The \texttt{science/wdmerger_I/} directory contains a number of example problems that we use
to assess the reliability of \texttt{CASTRO} in performing hydrodynamics simulations 
with self-gravity. This section includes a list of the existing problems 
as well as the instructions for building and running a problem.
